paper_replication

### 2021-12-15 paper_replication.Rmd
Update paper_replication.Rmd

countydem$county <- str_to_title(countydem$county)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
####### add in natality, maternalmortality, and infantdeath data #######
natality <- read.delim("natalitydata.txt")
maternalmortality <- read.delim("maternalmortality.txt")
infantdeath <- read.delim("infantdeathrecords.txt")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### recode restriction level and include all counties with abortion data in analysis ####

countydem <- countydem %>% mutate(hasabortiondata = case_when(is.na(AbortionRate2010) ~ 0, 
                                                              !(is.na(AbortionRate2010)) ~ 1))

countydemanalysis <- countydem %>% filter(hasabortiondata == 1)

summarytable <- countydem %>% group_by(state) %>% summarize(totalcounties = n())
usedcounties <- aggregate(AbortionRate2010 ~ state, data = countydem, function(x) {sum(!(is.na(x)))}, na.action = NULL)
summarytable <- left_join(summarytable, usedcounties, by = "state")
summarytable
summarytable %>% mutate(percent = AbortionRate2010/totalcounties) %>% kbl(col.names = c("State", "Total Counties", "Counties with Abortion Data in 2010", "Percent"), caption = "Table 1. Number of Counties with Abortion Data Included in Analysis by State") %>% kable_styling()
# names(countydem)
countydem <- countydem %>% mutate(Total = White + Black + Native.American + Asian + Hispanic, White.pct = White/Total, Black.pct = Black/Total, Native.American.pct = Native.American/Total, Asian.pct = Asian/Total, Hispanic.pct = Hispanic/Total, College.Grad.pct = College.Grad/Total)

countydem$hasabortiondatalabel <- factor(countydem$hasabortiondata, levels = c(1, 0), labels = c("Counties in States With Abortion Data", "Counties in States Without Abortion Data"))

@@

# The following function is based on 
# "Using the table1 Package to Create HTML Tables of Descriptive Statistics"
# by Benjamin Rich.  Available at:
# https://cran.r-project.org/web/packages/table1/vignettes/table1-examples.html#example-a-column-of-p-values
p_value_t_test <- function(x, ...){
    y <- unlist(x[1:2])
    g <- factor(rep(1:length(x[1:2]), times=sapply(x[1:2], length)))
    p_value <- t.test(y ~ g)$p.value %>% round(3) %>% as.character()
    p_value <- ifelse(p_value == '0', '< 0.001', p_value)
}

table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | hasabortiondatalabel, 
       data = countydem,
       extra.col = list(`P-value` = p_value_t_test),
       footnote = 'P-values are derived by two sample t-tests.'
       )

#calculate propensity scores
#include education this time
propensitywts <- glm(hasabortiondata ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008 + College.Grad.pct, data=countydem, family=binomial())
# summary(propensitywts)

@@

# plot of distribution of propensity scores 
ggplot(df, aes(x = ps, group = hasabortiondatalabel)) + geom_density(aes(fill = hasabortiondatalabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")

#run models, all 50 states, integer restrictions
countydemanalysis <- df %>% filter(hasabortiondata == 1)

ext_model_dist <- lm(AbortionRate2010 ~ totalrestrict + distancetoprovider + totalrestrict*distancetoprovider, data = countydemanalysis, weights = ps)
summ_ext_dist <- summary(ext_model_dist)

ext_model_no_dist <- lm(AbortionRate2010 ~ totalrestrict, data = countydemanalysis, weights = ps)
summ_ext_no_dist <- summary(ext_model_no_dist)

# Model Summaries (Note coefficients are per 1000 women)
table_ext_no_dist <- tibble(Characteristic = "Number of Types of Restrictive Legislation",
                  Beta = ext_model_no_dist$coefficients[2]*1000,
                  "p-value" = summ_ext_no_dist$coefficients[2,4]) %>% 
  kbl(caption = "Change in Abortions per 1000 Women in Model without Distances, all 50 States", digits = 3)
table_ext_no_dist
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
table_ext_dist <- tibble(Characteristic = c("Number of Types of Restrictive Legislation", 
                                            "Distance to Provider", 
                                            "Distance/Restriction Interaction"),
                  Beta = ext_model_dist$coefficients[2:4]*1000,
                  "p-value" = summ_ext_dist$coefficients[2:4,4]) %>% 
  kbl(caption = "Change in Abortions per 1000 Women in Model with Distances, all 50 States", digits = 3)
table_ext_dist
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
###further clean up maternaldeathrate, infantdeathrate, birthrate, and fertilityrate data ####
countydem$maternaldeathrate <- gsub(countydem$maternaldeathrate, pattern = "[()]", replacement = "")
countydem$maternaldeathrate <- gsub(countydem$maternaldeathrate, pattern = "Unreliable", replacement = "")
countydem$maternaldeathrate <- as.numeric(countydem$maternaldeathrate)
hist(countydem$maternaldeathrate)

@@

```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
### repeat analysis for infant death rate ###
countydem <- countydem %>% mutate(hasinfantdeathdata = case_when(is.na(countydem$infantdeathrate) ~ 0, 
                                                              !(is.na(countydem$infantdeathrate)) ~ 1))

countydeminfantdeathanalysis <- countydem %>% filter(hasinfantdeathdata == 1)

summarytable <- countydem %>% group_by(state) %>% summarize(totalcounties = n())
usedcounties <- aggregate(infantdeathrate ~ state, data = countydem, function(x) {sum(!(is.na(x)))}, na.action = NULL)
summarytable <- left_join(summarytable, usedcounties, by = "state")
summarytable %>% mutate(percent = infantdeathrate/totalcounties) %>% kbl(col.names = c("State", "Total Counties", "Counties with Data in 2010", "Percent"), caption = "Table 1. Number of Counties with Data Included in Analysis by State") %>% kable_styling()
# names(countydem)
countydem <- countydem %>% mutate(Total = White + Black + Native.American + Asian + Hispanic, White.pct = White/Total, Black.pct = Black/Total, Native.American.pct = Native.American/Total, Asian.pct = Asian/Total, Hispanic.pct = Hispanic/Total, College.Grad.pct = College.Grad/Total)

countydem$hasinfantdeathdatalabel <- factor(countydem$hasinfantdeathdata, levels = c(1, 0), labels = c("Counties in States With Data", "Counties in States Without Data"))

@@

print(table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | hasinfantdeathdatalabel, 
       data = countydem,
       extra.col = list(`P-value` = p_value_t_test),
       footnote = 'P-values are derived by two sample t-tests.'
       ))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#calculate propensity scores
#include education this time
propensitywts <- glm(hasinfantdeathdata ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008 + College.Grad.pct, data=countydem, family=binomial())

# plot of distribution of propensity scores 
plot1 <- ggplot(df, aes(x = ps, group = hasinfantdeathdatalabel)) + geom_density(aes(fill = hasinfantdeathdatalabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")
plot1

#run model
countydeminfantdeathanalysis <- df %>% filter(hasinfantdeathdata == 1)

model <- lm(infantdeathrate ~ totalrestrict + distancetoprovider + totalrestrict*distancetoprovider, data = countydeminfantdeathanalysis, weights = ps)
# summary(model)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
### repeat analysis for birth rate ###

countydem <- countydem %>% mutate(hasbirthratedata = case_when(is.na(countydem$Birth.Rate) ~ 0, 
                                                              !(is.na(countydem$Birth.Rate)) ~ 1))

countydembirthrateanalysis <- countydem %>% filter(hasbirthratedata == 1)

summarytable <- countydem %>% group_by(state) %>% summarize(totalcounties = n())
usedcounties <- aggregate(Birth.Rate ~ state, data = countydem, function(x) {sum(!(is.na(x)))}, na.action = NULL)
usedcounties
summarytable <- left_join(summarytable, usedcounties, by = "state")
summarytable
summarytable %>% mutate(percent = Birth.Rate/totalcounties) %>% kbl(col.names = c("State", "Total Counties", "Counties with Data in 2010", "Percent"), caption = "Table 1. Number of Counties with Data Included in Analysis by State") %>% kable_styling()
# names(countydem)
countydem <- countydem %>% mutate(Total = White + Black + Native.American + Asian + Hispanic, White.pct = White/Total, Black.pct = Black/Total, Native.American.pct = Native.American/Total, Asian.pct = Asian/Total, Hispanic.pct = Hispanic/Total, College.Grad.pct = College.Grad/Total)

countydem$hasbirthratedatalabel <- factor(countydem$hasbirthratedata, levels = c(1, 0), labels = c("Counties in States With Data", "Counties in States Without Data"))

print(table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | hasbirthratedatalabel, 
       data = countydem,
       extra.col = list(`P-value` = p_value_t_test),
       footnote = 'P-values are derived by two sample t-tests.'
       ))

#calculate propensity scores
#include education this time
propensitywts <- glm(hasbirthratedata ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008 + College.Grad.pct, data=countydem, family=binomial())
# summary(propensitywts)

# plot of distribution of propensity scores

plot1 <- ggplot(df, aes(x = ps, group = hasbirthratedatalabel)) + geom_density(aes(fill = hasbirthratedatalabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")
plot1

#run model
countydembirthrateanalysis <- df %>% filter(hasbirthratedata == 1)

model <- lm(Birth.Rate ~ totalrestrict + distancetoprovider + totalrestrict*distancetoprovider, data = countydembirthrateanalysis, weights = ps)
# summary(model)

test <- countydembirthrateanalysis %>% filter(ps > 0.9999999)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
### repeat analysis for fertility rate ###

countydem <- countydem %>% mutate(hasfertilityratedata = case_when(is.na(countydem$Fertility.Rate) ~ 0, 
                                                              !(is.na(countydem$Fertility.Rate)) ~ 1))

countydemfertilityrateanalysis <- countydem %>% filter(hasfertilityratedata == 1)

summarytable <- countydem %>% group_by(state) %>% summarize(totalcounties = n())
usedcounties <- aggregate(Fertility.Rate ~ state, data = countydem, function(x) {sum(!(is.na(x)))}, na.action = NULL)
usedcounties
summarytable <- left_join(summarytable, usedcounties, by = "state")
summarytable
summarytable %>% mutate(percent = Fertility.Rate/totalcounties) %>% kbl(col.names = c("State", "Total Counties", "Counties with Data in 2010", "Percent"), caption = "Table 1. Number of Counties with Data Included in Analysis by State") %>% kable_styling()
# names(countydem)
countydem <- countydem %>% mutate(Total = White + Black + Native.American + Asian + Hispanic, White.pct = White/Total, Black.pct = Black/Total, Native.American.pct = Native.American/Total, Asian.pct = Asian/Total, Hispanic.pct = Hispanic/Total, College.Grad.pct = College.Grad/Total)

countydem$hasfertilityratedatalabel <- factor(countydem$hasfertilityratedata, levels = c(1, 0), labels = c("Counties in States With Data", "Counties in States Without Data"))

print(table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | hasfertilityratedatalabel, 
       data = countydem,
       extra.col = list(`P-value` = p_value_t_test),
       footnote = 'P-values are derived by two sample t-tests.'
       ))

#calculate propensity scores
#include education this time
propensitywts <- glm(hasfertilityratedata ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008 + College.Grad.pct, data=countydem, family=binomial())
# summary(propensitywts)

p.score <- predict(propensitywts, countydem, type = "response")
df <- countydem
df$ps <- p.score
# plot of distribution of propensity scores

plot1 <- ggplot(df, aes(x = ps, group = hasfertilityratedatalabel)) + geom_density(aes(fill = hasfertilityratedatalabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")
print(plot1)

#run model
countydemfertilityrateanalysis <- df %>% filter(hasfertilityratedata == 1)

model <- lm(Fertility.Rate ~ totalrestrict + distancetoprovider + totalrestrict*distancetoprovider, data = countydemfertilityrateanalysis, weights = ps)
# summary(model)

>>>>

countydem$county <- str_to_title(countydem$county)
countydem$county <- gsub(countydem$county, pattern = "Doña Ana", replacement = "Dona Ana")

@@

```{r}
####### add in natality, maternalmortality, and infantdeath data #######
natality <- read.delim("natalitydata.txt")
maternalmortality <- read.delim("maternalmortality.txt")
infantdeath <- read.delim("infantdeathrecords.txt")

@@

```{r}
#### recode restriction level and include all counties with abortion data in analysis ####
countyanalysis <- function(varname) {
  countydem <- countydem %>% mutate(hasdata = case_when(is.na(countydem[[varname]]) ~ 0, 
                                                              !(is.na(countydem[[varname]])) ~ 1))
  countydemanalysis <- countydem %>% filter(hasdata == 1)
  summarytable <- countydem %>% group_by(state) %>% summarize(totalcounties = n())
  usedcounties <- aggregate(countydem[[varname]] ~ state, data = countydem, function(x) {sum(!(is.na(x)))}, na.action = NULL)
  summarytable <- left_join(summarytable, usedcounties, by = "state")
  print(summarytable %>% mutate(percent = summarytable[, 3]/totalcounties) %>% kbl(col.names = c("State", "Total Counties", "Counties with Data in 2010", "Percent"), caption = "Table 1. Number of Counties with Data Included in Analysis by State") %>% kable_styling())

  countydem$hasdatalabel <- factor(countydem$hasdata, levels = c(1, 0), labels = c("Counties in States With Data", "Counties in States Without Data"))

@@

  print(table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | hasdatalabel, 
       data = countydem,
       extra.col = list(`P-value` = p_value_t_test),
       footnote = 'P-values are derived by two sample t-tests.'
       ))

  #calculate propensity scores
  #include education this time
  propensitywts <- glm(hasdata ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008 + College.Grad.pct, data=countydem, family=binomial())

@@

  #plot of distribution of propensity scores 
  p1 <- ggplot(df, aes(x = ps, group = hasdatalabel)) + geom_density(aes(fill = hasdatalabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")
  print(p1)

  #run model
  countydemanalysis <- df %>% filter(hasdata == 1)

  model <- lm(countydemanalysis[[varname]] ~ totalrestrict + distancetoprovider + totalrestrict*distancetoprovider, data = countydemanalysis, weights = ps)
  return(summary(model))
}

countyanalysis("AbortionRate2010")
```

```{r}
###further clean up maternaldeathrate, infantdeathrate, birthrate, and fertilityrate data ####
countydem$maternaldeathrate <- gsub(countydem$maternaldeathrate, pattern = "[()]", replacement = "")
countydem$maternaldeathrate <- gsub(countydem$maternaldeathrate, pattern = "Unreliable", replacement = "")
countydem$maternaldeathrate <- as.numeric(countydem$maternaldeathrate)
hist(countydem$maternaldeathrate)

@@

```{r}

largecountyanalysis <- function(varname) {
  largecountydem <- countydem %>% filter(Total >= 250000)
  largecountydem <- largecountydem %>% mutate(hasdata = case_when(is.na(largecountydem[[varname]]) ~ 0, 
                                                              !(is.na(largecountydem[[varname]])) ~ 1))
  largecountydemanalysis <- largecountydem %>% filter(hasdata == 1)
  summarytable <- countydem %>% group_by(state) %>% summarize(totalcounties = n())
  usedcounties <- aggregate(largecountydem[[varname]] ~ state, data = largecountydem, function(x) {sum(!(is.na(x)))}, na.action = NULL)
  summarytable <- left_join(summarytable, usedcounties, by = "state")
  print(summarytable %>% mutate(percent = summarytable[, 3]/totalcounties) %>% kbl(col.names = c("State", "Total Counties", "Counties with Data in 2010", "Percent"), caption = "Table 1. Number of Counties with Data Included in Analysis by State") %>% kable_styling())

  largecountydem$hasdatalabel <- factor(largecountydem$hasdata, levels = c(1, 0), labels = c("Counties in States With Data", "Counties in States Without Data"))

  label(largecountydem$Women) = "Women"
  label(largecountydem$White.pct) = "White"
  label(largecountydem$Black.pct) = "Black"
  label(largecountydem$Native.American.pct) = "Native American"
  label(largecountydem$Asian.pct) = "Asian"
  label(largecountydem$Hispanic.pct) = "Hispanic"
  label(largecountydem$Median.Income) = "Median Income"
  label(largecountydem$College.Grad.pct) = "College Graduates"
  label(largecountydem$percentdem2008) = "Voting for the Democratic candidate in the most recent presidential election"

  units(largecountydem$Women) = "No."
  units(largecountydem$White.pct) = "%"
  units(largecountydem$Black.pct) = "%"
  units(largecountydem$Native.American.pct) = "%"
  units(largecountydem$Asian.pct) = "%"
  units(largecountydem$Hispanic.pct) = "%"
  units(largecountydem$Median.Income) = "$"
  units(largecountydem$College.Grad.pct) = "%"
  units(largecountydem$percentdem2008) = "%"

  print(table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | hasdatalabel, 
       data = largecountydem,
       ))

  #calculate propensity scores
  #include education this time
  propensitywts <- glm(hasdata ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008 + College.Grad.pct, data=largecountydem, family=binomial())

  p.score <- predict(propensitywts, largecountydem, type = "response")
  df <- largecountydem
  df$ps <- p.score

  #plot of distribution of propensity scores 
  p1 <- ggplot(df, aes(x = ps, group = hasdatalabel)) + geom_density(aes(fill = hasdatalabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")
  print(p1)

  #run model
  largecountydemanalysis <- df %>% filter(hasdata == 1)

  model <- lm(largecountydemanalysis[[varname]] ~ totalrestrict + distancetoprovider + totalrestrict*distancetoprovider, data = largecountydemanalysis, weights = ps)
  return(summary(model))
}

largecountyanalysis("infantdeathrate")

```{r}
largecountyanalysis("infantdeathrate")
```

```{r}
largecountyanalysis("Birth.Rate")
```

```{r}
largecountyanalysis("Fertility.Rate")
```

```{r}
#add in state level maternaldeathrate, infantdeathrate, birthrate, and fertilityrate data ####

statelevelnatality <- read.delim("statelevelnatality.txt")
statelevelinfantdeaths <- read.delim("statelevelinfantdeaths.txt")
statelevelfetaldeaths <- read.delim("statelevelfetaldeaths.txt")
statelevelmaternalmortality <- read.delim("statelevelmaternalmortality.txt")

statelevelnatality <- statelevelnatality %>% select(State, Birth.Rate, Fertility.Rate)
statelevelinfantdeaths <- statelevelinfantdeaths %>% select(State, Death.Rate)
statelevelfetaldeaths <- statelevelfetaldeaths %>% select(Standard.Residence.States, Percent.of.Total.Deaths) %>% rename(State = Standard.Residence.States, Pct.Fetal.Deaths = Percent.of.Total.Deaths)
statelevelmaternalmortality <- statelevelmaternalmortality %>% select(State, X..of.Total.Deaths) %>% rename(Pct.Maternal.Deaths = X..of.Total.Deaths)

statedem <- countydem %>% group_by(state) %>% summarize(AvgWomen = mean(Women, na.rm = TRUE), AvgWhite.pct = mean(White.pct, na.rm = TRUE), AvgBlack.pct = mean(Black.pct, na.rm = TRUE), AvgNative.American.pct = mean(Native.American.pct, na.rm = TRUE), AvgAsian.pct = mean(Asian.pct, na.rm = TRUE), AvgHispanic.pct = mean(Hispanic.pct, na.rm = TRUE), AvgCollege.Grad.pct = mean(College.Grad.pct, na.rm = TRUE), AvgMedian.Income = mean(Median.Income, na.rm = TRUE), AvgDem2008.pct = mean(percentdem2008, na.rm = TRUE), AvgDistancetoProvider = mean(distancetoprovider, na.rm = TRUE), TotalRestrictions = mean(totalrestrict, na.rm = TRUE), AvgAbortionRate2010 = mean(AbortionRate2010, na.rm = TRUE)) %>% rename(State = state)

statedem <- left_join(statedem, statelevelnatality, by = c("State"))
statedem <- left_join(statedem, statelevelinfantdeaths , by = c("State"))
statedem <- left_join(statedem, statelevelfetaldeaths, by = c("State"))
statedem <- left_join(statedem, statelevelmaternalmortality, by = c("State"))

for (i in 1:ncol(statedem)) {
  statedem[[i]][is.nan(statedem[[i]])] <- NA
}

statedem$Pct.Maternal.Deaths <- na_if(statedem$Pct.Maternal.Deaths, "Suppressed")
statedem$Pct.Maternal.Deaths <- gsub(statedem$Pct.Maternal.Deaths, pattern = "%", replacement = "")
statedem$Pct.Maternal.Deaths <- as.numeric(statedem$Pct.Maternal.Deaths)

```{r}
###make function for extended analysis###
stateanalysis <- function(varname) {
  statedem <- statedem %>% mutate(hasdata = case_when(is.na(statedem[[varname]]) ~ 0, 
                                                              !(is.na(statedem[[varname]])) ~ 1))
  statedemanalysis <- statedem %>% filter(hasdata == 1)
  statedem$hasdatalabel <- factor(statedem$hasdata, levels = c(1, 0), labels = c("States With Data", "States Without Data"))

  label(statedem$AvgWomen) = "Average Women"
  label(statedem$AvgWhite.pct) = "Average White"
  label(statedem$AvgBlack.pct) = "Average Black"
  label(statedem$AvgNative.American.pct) = "Average Native American"
  label(statedem$AvgAsian.pct) = "Average Asian"
  label(statedem$AvgHispanic.pct) = "Average Hispanic"
  label(statedem$AvgMedian.Income) = "Average Median Income"
  label(statedem$AvgCollege.Grad.pct) = "Average College Graduates"
  label(statedem$AvgDem2008.pct) = "Average Voting for the Democratic candidate in the most recent presidential election"

  units(statedem$AvgWomen) = "No."
  units(statedem$AvgWhite.pct) = "%"
  units(statedem$AvgBlack.pct) = "%"
  units(statedem$AvgNative.American.pct) = "%"
  units(statedem$AvgAsian.pct) = "%"
  units(statedem$AvgHispanic.pct) = "%"
  units(statedem$AvgMedian.Income) = "$"
  units(statedem$AvgCollege.Grad.pct) = "%"
  units(statedem$AvgDem2008.pct) = "%"

@@

  print(table1(~ AvgWomen + AvgWhite.pct + AvgBlack.pct + AvgNative.American.pct + AvgAsian.pct + AvgHispanic.pct + AvgMedian.Income + AvgCollege.Grad.pct + AvgDem2008.pct | hasdatalabel, 
       data = statedem,
       extra.col = list(`P-value` = p_value_t_test),
       footnote = 'P-values are derived by two sample t-tests.'
       ))

  #calculate propensity scores
  #include education this time
  propensitywts <- glm(hasdata ~ AvgWhite.pct + AvgBlack.pct + AvgNative.American.pct + AvgAsian.pct + AvgHispanic.pct + AvgMedian.Income + AvgCollege.Grad.pct + AvgDem2008.pct, data=statedem, family=binomial())

  p.score <- predict(propensitywts, statedem, type = "response")
  df <- statedem
  df$ps <- p.score

  #plot of distribution of propensity scores

  plot1 <- ggplot(df, aes(x = ps, group = hasdatalabel)) + geom_density(aes(fill = hasdatalabel), alpha = 0.2) +
    xlab('Probability of Being in the Analysis') +
    ggtitle('Propensity Score Distribution by Group') +
    scale_fill_discrete('') +
    theme(legend.position = 'bottom', legend.direction = 'vertical') +
    ylab("Density")
  print(plot1)

  #run model
  statedemanalysis <- df %>% filter(hasdata == 1)

  model <- lm(statedemanalysis[[varname]] ~ TotalRestrictions + AvgDistancetoProvider, data = statedemanalysis, weights = ps)
  summary(model)
}

@@

```{r}
stateanalysis("AvgAbortionRate2010")
```

```{r}
stateanalysis("Birth.Rate")
```

```{r}
stateanalysis("Fertility.Rate")
```

```{r}
stateanalysis("Death.Rate")
```

```{r}
stateanalysis("Pct.Fetal.Deaths")
```

```{r}
stateanalysis("Pct.Maternal.Deaths")
```
